---
title: "Lab 10"
author: "Mia Guarnieri"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(usethis)
library(janitor)

library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

# beepr package beeps

Use the function `beep()` in the beepr package to make an audio alert when your code is done running.

Can make other sounds too! Sounds correlate to numbers.

`seq()` will make a sequence
`rev()` will reverse it

```{r, eval = FALSE}
for (i in rev(seq(1:9999))) {
  
  print(paste(i, "bottles of beer on the wall"))
  
}

# beep(4)
#eval = FALSE means r will not even evaluate this code
```

## praise and cowsay

Packages built with a single purpose: to be kind and fun

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!") #will keep capitalization

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

use cowsay::say() to make a character say something to you

```{r}
say("You are great!", by = "stretchycat")
```


Navigate to r profile: in Console, usethis::edit_r_profile()

To make this a version-controlled project in git..

usethis::use_git()

THEN

usethis::use_github() to connect to repo


# paletteer to access thousands of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("palettetown::nuzleaf")
```






